The binary liquid model for gravity-driven microchannel simulations

### 2010-11-24 Text/paper.tex
Revised all text. Need to wait Sasha's sketch.

\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{color}

@@

We illustrate the procedure for the capillary number
$0.05$. As was pointed out earlier, the film thickness in that case is $6$ percent of the effective
channel $H_{\mathrm{eff}}$.
Note that in the case of the half-way bounce-back walls \cite{yu} which are used in the
simulations one needs to calculate the film thickness as:
\begin{equation}
\delta=(\phi_0-0.5)/(N_y-2),
\end{equation}
where $\phi_0$ is the grid coordinate where phase field is $0$, $N_y-2$
is related to the effective channel height. That can be cleared out by the following explanations.
If the grid number in the vertical direction is $N_y$ then one has $N_y-1$ regions which represent
domain. The effective wall location is in the middle between bounce-back and fluid nodes giving
overall $N_y-2$ representing the channel width. Note that it is a big
simplification to impose the boundary in the middle beetween the bounce-back
node and the fluid node which give rise to the viscosity dependent location of
the wall \cite{ginzburg-multireflection}, however the effective location of the wall for the
multiphase models to the best authors' knowledge is not yet derived. In the case of $\delta=0.06$
the
initial grid size is $N_y=102$, which gives the horizontal grid size as $N_x-1=15(N_y-2)=1500$.
The bubble is initialized as a rectangular box with coordinates
$y=7\dots N_y-8$, $x=\frac{N_x}{3}\dots \frac{2 N_x}{3}$ and phase
$\phi_{\mathrm{bubble}}=-1$. All other nodes are initialized with the phase field
$\phi=1$. The force gradient can be estimated through the Poiseuille
profile formula, Eq.~\ref{poiseuille:velocity:center}, and it equals
$1.508 \cdot 10^{-6}$ lattice units.

After choosing the reference parameters, the grid refinement procedure
needs to keep the macroscopic parameters constant.  Therefore the simulations
were performed with grid numbers $N_y=102,127,152,177,202,227$, corresponding to the
effective channels widths  $H_{\mathrm{eff}}=100,125,150,175,200,225$,
$N_x=1501,1876,2251,2626,3001,3376=15
H_{\mathrm{eff}}+1$. It is easy to check
that keeping all liquid viscosities the same yields the following quantity to
be independent of grid size
$H_{\mathrm{eff}}^2\frac{\mathrm{d}P}{\mathrm{d}x}=(N_y-2)^2\frac{\mathrm{d}P}{\mathrm{d}
x } = \mathrm{const}$. We performed a number of simulations for the prescribed grids.
The unified scaled profiles are shown in Fig. \ref{fig:grid:profiles}. One can
see the visual results converge for $H_{\mathrm{eff}}\geq 175$. The calculated widths
are $0.0606$,$0.0618$,$0.0617$,$0.0629$,$0.0624$,$0.0624$. We accept the
convergent results for grids larger than $H_{\mathrm{eff}}=175$. However, one can see
that with proper initialization techniques, large enough time and the wall
wettability, results are different only in the 3rd digit even for
underresolved film widths. To calculate how well the interface thickness is
resolved, the ratio of the interface thickness to the film width thickness is calculated. The
interface itself occupies approximately $5 \xi$, where
$\xi=\sqrt{k/A}=1$. Let us calculate the interface width ratio to the film
thickness as
$5\xi/H_{\mathrm{film}}$: $0.824$, $0.646$,  $0.539$, $0.453$,
$0.400$, $0.355$. Therefore, one needs to
resolve the interface as $40-50$ percent of the
expected film width for simulations to be convergent. We further examine the
velocities in the center of the bubble to calculate the Capillary number. The
calculated numbers are $0.0041$, $0.0041$,$0.0040$,$0.0040$,$0.0041$,$0.0039$.
This corresponds to the average capillary number of $0.07$, which is slightly
larger than the expected capillary number. The corresponding error can be
attributed to the density and viscosity ratios which are much larger in the
Bretherton problem.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Grid/norm_grid_profs.eps}
\caption{Grid-refined profiles for the effictive
channel widths
$H_{\mathrm{eff}}=100,125,150,175,200,225$.One can see
convergent results even for the underresolved film
thickness.\label{fig:grid:profiles}}
\end{figure}
%Here will be a consolidated table
\begin{table}

\end{table}

\subsection{The influence of the wall gradient}
The simulation results should not depend on the wall wettability. Wettability is defined
through the phase gradient \cite{pooley-contact}, $\partial_n \phi$.  We took a large
enough grid resolution in order for simulations to be consistent -- the grid size was
$177 \times 2626$ and the initial film width was
$12$ lattice boltzmann units, which corresponds to the predicted film thickness.
We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For the
given wall gradients the values of interface thickness values are
$0.0633$,$0.0634$,$0.0634$,$0.0634$,$0.0634$,$0.0634$,$0.0633$,$0.0632$,
$0.0631$. The results are different in 4th digit. For the wall gradients $0.8$
and $1.0$ the
simulations are unstable. One can see the simulated profiles in Fig.
\ref{fig:gradients:profiles}. Negative values of the phase gradient are
preferable, since the phase of the liquid adjacent to the wall has the value of $1$.
The phase values near the wall are above $1$ and do not interact
with the bubble which has phase value $-1$.  In case of positive
gradients the values near the wall are below $1$, and the gradient profile can
fuse with the values of the gas phase as, giving rise to an unphysical wall stickyness.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Wall/phase_grad_profiles.eps}
\caption{Phase profiles for different wall gradients. One can see that if the width
is properly resolved then the wettability of the wall does affect the film thickness.
\label{fig:gradients:profiles}
}
\end{figure}
Another question which arises is the influence of the wall gradient on the bubble velocity and the
corresponding capillary number. The shear stress controlled by the wall phase gradient changes the
effective velocity near the wall, thus changing the bubble velocity as well.
One can see that if the film thickness is resolved properly the influence of the wall gradient can
be neglected. Fig. \ref{fig:velocities:wall:gradient} shows the center bubble velocity for different
gradients. The average relative error around the mean velocity is $0.1\%$.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Wall/velocities_grad_profiles.eps}
\caption{The center bubble velocity versus the phase gradient. One can neglect the influence of
the wall once the film is properly resolved.
\label{fig:velocities:wall:gradient}
}
\end{figure}

\subsection{Capillary number region}
The purpose of this section is to validate the correlations of
\citet{giavedoni-numerical}, Fig. \ref{fig:giavedoni:planar}, and
\citet{heil-bretherton}, Fig. \ref{fig:heil:planar}, for a range of capillary
numbers. Because of limited computational resources, we skip the
small capillary numbers and compare the film thickness over the capillary number
range from $0.03$ to $0.8$, which is a computationally reasonable task.  For the
benchmark
results we
suggest the following Capillary numbers:
\begin{equation}
0.03,0.05,0.08,0.1,0.2,0.4,0.6,0.8\, .
\end{equation}
The corresponding approximate film widths from \cite{giavedoni-numerical} are as
follows:
\begin{equation}
0.04,0.06,0.08,0.1,0.12,0.13,0.15\,.
\end{equation}
To perform numerical simulations we refer
to the grid refinement section where we established that the interface width should be
at most $50$ percent of the interface width.  We therefore choose the grid to be
$202 \times 3001$. $5$ lattice Boltzmann units do not occupy more than $60$
percent of the effective width. Because the simulation get unstable with
smaller grids and larger gradients, all the capillary number simulations were
performed on the chosen grid. To properly initialize the force gradient, the
proportionality law was utilized. The forcing
$6 \cdot 10^{-6}/16$ was chosen to obtain the predicted capillary
number $0.005$. The forcing for other grids can be obtained using
simple correlations:
\begin{equation}
\begin{aligned}
&Ca_{\mathrm{lit}} \propto U_{\mathrm{bubble}}\\
&U_{\mathrm{bubble}} \propto \frac{\mathrm{d}P}{\mathrm{d}x} N_y^2\\
&Ca_{\mathrm{lit}} \propto \frac{\mathrm{d}P}{\mathrm{d} x} N_y^2 \text{ or }\\
&\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{\Ca_{\mathrm{lit}}}{N_y^2},
\end{aligned}
\end{equation}
where the index ,,lit'' stands for the predicted capillary number
\cite{giavedoni-numerical,heil-bretherton}. The grid number $N_y$ is not
involved because all simulations are conducted on the same grid.
The pressure gradient can be obtained through the capillary numbers
ratio:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d} x}=6 \cdot 10^{-6}/16 \frac{Ca_{\mathrm{lit}}}{0.05}
\end{equation}
The film width is initialized through the capillary numbers ratio as well:
\begin{equation*}
w=12 \frac{Ca_{\mathrm{lit}}}{0.05}
\end{equation*}
The results were obtained after $2\cdot10^5$ steps. The following film thicknesses were
calculated: $0.042$,$0.066$, $0.085$, $0.077$, $0.123$, $0.153$, $0.164$, $0.173$ with
the corresponding bubble center velocities $0.0022$, $0.0041$, $0.0068$, $0.0055$,
$0.0185$, $0.0388$, $0.0592$, $0.0782$. Based on the obtained center velocities,
the capillary numbers are calculated as
$0.039$,$0.072$,$0.120$,$0.098$,$0.328$,$0.686$,$1.046$,$1.383$. These
capillary numbers are overpredicted but the obtained widths are overpredicted
as well due to the improper body force imposement, because the assumption of Poiseuille flow is not
valid. If one needs to obtain the desired capillary number, the shooting method for the forcing is
necessary starting as the Poiseuille pressure gradient force as the initial condition. We extracted
data from
\cite{giavedoni-numerical,heil-bretherton} and compared it the results of our
simulations, which are shown in Fig. \ref{fig:capillary:comparison}.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Capillary/capillaries_comparison.eps}
\caption{A comparison between simulation results and results from
\cite{giavedoni-numerical} and \cite{heil-bretherton}. One can see a
reasonable agreement. The plots depict the film thickness as a function of the
the capillary number.\label{fig:capillary:comparison}}
\end{figure}

@@

Next, we investigated the qualitative variation of the film thickness over the bubble length.
Though there are simulations for the bubble length for the two-dimensional case, due to
the presentation of data it is hard to extract numerical values from the plots. One can see bubble lengths
variations for the two-dimensional simulations for the range of capillary numbers in Fig.
\ref{fig:sehgal:bubble:length}.
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/Bubble/bubble_length.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/Bubble/bubble_sehgal.eps}\\
\caption{The qualitative comparison for the film thickness across
the bubble length. Right (courtesy of \citet{sehgal-microchannel}),
left (present simulations).\label{fig:sehgal:bubble:length}}
\end{figure}
One can see a qualitative agreement, i.e. the thickness increases towards the front meniscus and
rapidly decreases towards the rear meniscus. This shape sometimes is called as a "bullet" shape.

@@

\section{Conclusion}
This work presents numerical tips and a benchmark for the
Bretherton/Taylor problem using the binary liquid lattice Botlzmann method. The
results show consistency with the previously published numerical results obtained
using other methods. Though our results are specific to the binary liquid lattice
Botlzmann method, the numerical hints and procedures can be used for any
continuous interface method.  We hope this work will prove to be valuable for
people simulating microchannel flows.

\bibliographystyle{unsrtnat}
\bibliography{paper}

>>>>

\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{color}
\usepackage{tabularx}

@@

We illustrate the procedure for the capillary number
$0.05$. As was pointed out earlier, the film thickness in that case is $6$ percent of the effective
channel $H_{\mathrm{eff}}$.
Note that in the case of the half-way bounce-back walls \cite{yu} which are used in the
simulations one needs to calculate the film thickness as:
\begin{equation}
\delta=(\phi_0-0.5)/(N_y-2),
\end{equation}
where $\phi_0$ is the grid coordinate where phase field is $0$, $N_y-2$
is related to the effective channel height. That can be cleared out by the following explanations.
If the grid number in the vertical direction is $N_y$ then one has $N_y-1$ regions which represent
domain. The effective wall location is in the middle between bounce-back and fluid nodes giving
overall $N_y-2$ representing the channel width. Note that it is a big
simplification to impose the boundary in the middle beetween the bounce-back
node and the fluid node which give rise to the viscosity dependent location of
the wall \cite{ginzburg-multireflection}, however the effective location of the wall for the
multiphase models to the best authors' knowledge is not yet derived. In the case of $\delta=0.06$
the
initial grid size is $N_y=102$, which gives the horizontal grid size as $N_x=15(N_y-2)=1500$.
The bubble is initialized as a rectangular box with coordinates
$y=7\dots N_y-8$, $x=\frac{N_x}{3}\dots \frac{2 N_x}{3}$ and phase
$\phi_{\mathrm{bubble}}=-1$. All other nodes are initialized with the phase field
$\phi=1$. The force gradient can be estimated through the Poiseuille
profile formula, Eq.~\ref{poiseuille:velocity:center}, and it equals
$1.508 \cdot 10^{-6}$ lattice units.

After choosing the reference parameters, the grid refinement procedure
needs to keep the macroscopic parameters constant.  It is easy to check
that it yields the following quantity to
be independent of grid size
$H_{\mathrm{eff}}^2\frac{\mathrm{d}P}{\mathrm{d}x}=(N_y-2)^2\frac{\mathrm{d}P}{\mathrm{d}
x } = \mathrm{const}$. We performed a number of simulations for the prescribed grids. The
simulations in terms of grid numbers $N_x$, $N_y$, the film thickness $\delta$, center bubble
velocity $U_{bubble}$ are summarized in Table \ref{table:parameters:grid:refinement}.
The unified scaled profiles are shown in Fig. \ref{fig:grid:profiles}. One can
see the visual results converge for $H_{\mathrm{eff}}\geq 175$. However, one can see
that with proper initialization techniques, large enough time and the wall
wettability, results are different only in the 3rd digit even for
underresolved film widths. To calculate how well the interface thickness is
resolved, the ratio of the interface thickness to the film width thickness is calculated. The
interface itself occupies approximately $5 \xi$, where
$\xi=\sqrt{k/A}=1$. The ratio of the interface width to the film thickness $5\xi/H_{\mathrm{film}}$
 is shown in Table \ref{table:parameters:grid:refinement}. Based on results one can conclude that
 the interface needs to be resolved as $40-50$ percent of the
expected film width for simulations to be convergent. We further examine the
velocities in the center of the bubble to calculate the Capillary number. One can see from Table
\ref{table:parameters:grid:refinement} that the bubble velocities are pretty consistent and the
calculated capillary number corresponding to those values is $0.07$, which is slightly
larger than the expected capillary number. The corresponding error can be
attributed to the density and viscosity ratios which are much larger in the
Bretherton problem and Poiseuille profile body force initialization.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Grid/norm_grid_profs.eps}
\caption{Grid-refined profiles for the effective
channel widths
$H_{\mathrm{eff}}=100,125,150,175,200,225$.$\delta$ is scaled on $H_{eff}$ and $\delta=0$
corresponds to the wall location. The profiles were taken at $x=14$ nondimensional coordinate.
Capillary number is $Ca=0.05$. Capillary number obtained from simulations $Ca=0.07$. One can
see
convergent results even for the underresolved film
thickness.\label{fig:grid:profiles}}
\end{figure}
%Here will be a consolidated table
\begin{table}
\begin{tabularx}{0.97\textwidth}{|X|X|X|X|X|X|}
\hline
$N_x$&$N_y$&$\delta$&$U_{bubble}$&$\frac{5\xi}{H_{\mathrm{film}}}$&$N_{iter}$\\
\hline
$1500$&$102$&$0.0694$&$0.0041$&$0.824$&$200000$\\
\hline
$1875$&$127$&$0.0688$&$0.0041$&$0.646$&$250000$\\
\hline
$2250$&$152$&$0.0676$&$0.0040$&$0.539$&$300000$\\
\hline
$2625$&$177$&$0.0679$&$0.0040$&$0.453$&$350000$\\
\hline
$3000$&$202$&$0.0668$&$0.0041$&$0.400$&$400000$\\
\hline
$3375$&$227$&$0.0663$&$0.0039$&$0.355$&$450000$\\
\hline
\end{tabularx}
\caption{The parameters and results for studying grid resolution simulations. Domain simulated is
of size $N_x\, \mathrm{x}\, N_y$. $U_{bubble}$ is center
bubble velocity measured at the scaled to $H_eff$ $x=14.0$.
$5\xi$ is the interface thickness. $H_{\mathrm{film}}=\delta (N_y-2)$ is the size of the film in
lattice Boltzmann units. $Ca=0.05$ was taken to initialize the simulation.
\label{table:parameters:grid:refinement}}
\end{table}

\subsection{The influence of the wall gradient}
The simulation results should not depend on the wall wettability. Wettability is defined
through the phase gradient \cite{pooley-contact}, $\partial_n \phi$.  We took a large
enough grid resolution in order for simulations to be consistent -- the grid size was
$177 \times 2626$ and the initial film width was
$12$ lattice boltzmann units, which corresponds to the predicted film thickness.
We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The parameters are summarized in Table
\ref{table:parameters:wall:gradient}. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For 
given wall gradients the values of interface thickness values are of $0.2\%$ relative accuracy.  For
the wall gradients $0.8$
and $1.0$ the
simulations are unstable. One can see the simulated profiles in Fig.
\ref{fig:gradients:profiles}. The latter shows that the negative wall gradient values cause 
unphysical phase values more than $1.0$ near the wall. One should attribute them to the numerical
imposement of wall gradients. Therefore, they do not spoil numerical scheme as whole. Note that
negative values of the phase gradient are
preferable, since the phase of the liquid adjacent to the wall has the value of $1$.
The phase values near the wall are above $1$ and do not interact
with the bubble which has phase value $-1$.  In case of positive
gradients the values near the wall are below $1$, and the gradient profile can
fuse with the values of the gas phase. This case is attributed when to the slug flow when gas
touches the wall.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Wall/phase_grad_profiles.eps}
\caption{Phase profiles for different wall gradients. One can see that if the width
is properly resolved then the wettability of the wall does affect the film thickness. The
simulations were conducted for $200,000$ iterations. The measured profile was taken at the
nondimensional coordinate scaled to $H_{\mathrm{eff}}$ as $x=11.42$. $Ca=0.05$ was taken to
initialize simulation.
\label{fig:gradients:profiles}
}
\end{figure}

Another question which arises is the influence of the wall gradient on the bubble velocity and the
corresponding capillary number. The shear stress controlled by the wall phase gradient changes the
effective viscosity near the wall, thus changing the bubble velocity as well. If viscosity ratio is
high enough then the free surface motion of the bubble should not be dependent on the shear stress
near the wall.
One can see that if the film thickness is resolved properly the influence of the wall gradient can
be neglected. The center bubble velocities are presented in Table
\ref{table:parameters:wall:gradient}. 
%Fig. \ref{fig:velocities:wall:gradient} shows the center bubble velocity for different
%gradients. 
The average relative error around the mean velocity is $0.1\%$.
% Uncomment if you need this picture
% \begin{figure}
% \includegraphics[width=0.97\textwidth]{Figures/Wall/velocities_grad_profiles.eps}
% \caption{The center bubble velocity versus the phase gradient. One can neglect the influence of
% the wall once the film is properly resolved.
% \label{fig:velocities:wall:gradient}
% }
% \end{figure}
\begin{table}
\begin{tabularx}{\textwidth}{|X|X X X X X X X X X X X|}
\hline
$\scriptstyle \partial_n \phi$& $\scriptstyle -1.0$& $\scriptstyle -0.8$&
$\scriptstyle -0.6$&$\scriptstyle -0.4$&$\scriptstyle -0.2$&$\scriptstyle
0.0$&$\scriptstyle 0.2$&$\scriptstyle 0.4$&$\scriptstyle 0.6$&$\scriptstyle 0.8$&$\scriptstyle
1.0$\\
\hline
$\scriptstyle \delta$& $\scriptstyle 0.0633$& $\scriptstyle 0.0634$& $\scriptstyle 0.0634$&
$\scriptstyle 0.0634$& $\scriptstyle 0.0634$& $\scriptstyle 0.0634$& $\scriptstyle 0.0633$&
$\scriptstyle 0.0632$& $\scriptstyle 0.0631$ &$\scriptstyle \mathrm{N/A}$&$\scriptstyle
\mathrm{N/A}$\\
\hline
$\scriptstyle U_{b}$ &$\scriptstyle 0.0041$& $\scriptstyle 0.0042$& $\scriptstyle 0.0042$
&$\scriptstyle 0.0042$ & $\scriptstyle 0.0041$& $\scriptstyle 0.0041$ & $\scriptstyle 0.0042$ &
$\scriptstyle 0.0042$ & $\scriptstyle 0.0042$ & $\scriptstyle \mathrm{N/A}$ &$\scriptstyle
\mathrm{N/A}$\\
\hline
\end{tabularx}
\caption{The parameters and results for studying wall gradient simulations. $U_{b}$ stands for the
center bubble velocity. $\delta$ is the interface thickness. $\partial_n \phi$ is the phase
gradient near the wall responsible for hydrophilic and hydrophobic behavior. The results are
calculated at nondimensional $x=11.42$ after $200000$ time iterations. $Ca=0.05$ was taken to
initialize simulation.
\label{table:parameters:wall:gradient}}
\end{table}

\subsection{Capillary number region}
The purpose of this section is to validate the correlations of
\citet{giavedoni-numerical}, Fig. \ref{fig:giavedoni:planar}, and
\citet{heil-bretherton}, Fig. \ref{fig:heil:planar}, for a range of capillary
numbers. Because of limited computational resources, we skip the
small capillary numbers and compare the film thickness over the capillary number
range from $0.03$ to $0.8$, which is a computationally reasonable task.  
To perform numerical simulations we refer
to the grid refinement section where we established that the interface width should be
at most $50$ percent of the interface width.  We therefore choose the grid to be
$202 \times 3001$. $5$ lattice Boltzmann units do not occupy more than $60$
percent of the effective width. Because the simulation get unstable with
smaller grids and larger gradients, all the capillary number simulations were
performed on the chosen grid. To properly initialize the force gradient, the
proportionality law was utilized. The forcing
$6 \cdot 10^{-6}/16$ was chosen to obtain the predicted capillary
number $0.05$. The forcing for other grids can be obtained using
simple correlations:
\begin{equation}
\begin{aligned}
&Ca_{\mathrm{lit}} \propto U_{\mathrm{bubble}}\\
&U_{\mathrm{bubble}} \propto \frac{\mathrm{d}P}{\mathrm{d}x} N_y^2\\
&Ca_{\mathrm{lit}} \propto \frac{\mathrm{d}P}{\mathrm{d} x} N_y^2 \text{ or }\\
&\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{\Ca_{\mathrm{lit}}}{N_y^2},
\end{aligned}
\end{equation}
where the subscript ,,lit'' stands for the predicted capillary number
\cite{giavedoni-numerical,heil-bretherton}. The grid number $N_y$ is not
involved because all simulations are conducted on the same grid.
The pressure gradient can be obtained through the capillary numbers
ratio:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d} x}=6 \cdot 10^{-6}/16 \frac{Ca_{\mathrm{lit}}}{0.05}
\end{equation}
The film width is initialized through the capillary numbers ratio as well:
\begin{equation*}
w=12 \frac{Ca_{\mathrm{lit}}}{0.05}
\end{equation*}
The results were obtained after $2\cdot10^5$ steps. Simulation results are presented in Table
\ref{table:parameters:capillary:number}. One can see that the calculated
capillary numbers are overpredicted but the obtained widths are overpredicted
as well due to the improper body force imposement, because of the Poiseuille flow assumption. If one
needs to obtain the desired capillary number, the shooting method for the forcing is
necessary starting as the Poiseuille pressure gradient force as the initial condition. We extracted
results of 
\citet{giavedoni-numerical} and \citet{heil-bretherton} and compared them with our results, shown
in Fig. \ref{fig:capillary:comparison}.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Capillary/capillaries_comparison.eps}
\caption{A comparison between simulation results and results of
\citet{giavedoni-numerical} and \citet{heil-bretherton}. One can see a
reasonable agreement. The plots depict the film thickness as a function of the
the capillary number.\label{fig:capillary:comparison}}
\end{figure}

\begin{table}
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
\hline
$Ca_{\mathrm{lit}}$&$\delta_{\mathrm{lit}}$&$x$&$\delta$&$U_b$&$Ca$\\
\hline
$0.03$&$0.04$&$10.0$&$0.042$&$0.0022$&$0.039$\\
\hline
$0.05$&$0.06$&$11.0$&$0.066$&$0.0041$&$0.072$\\
\hline
$0.08$&$0.08$&$13.0$&$0.085$&$0.0068$&$0.120$\\
\hline
$0.1$&$0.1$&$12.5$&$0.077$&$0.0055$&$0.098$\\
\hline
$0.2$&$0.12$&$5.5$&$0.123$&$0.0185$&$0.328$\\
\hline
$0.4$&$0.13$&$4.7$&$0.153$&$0.0388$&$0.686$\\
\hline
$0.6$&$0.15$&$3.0$&$0.164$&$0.0592$&$1.046$\\
\hline
$0.8$&$0.16$&$1.7$&$0.173$&$0.0782$&$1.383$\\
\hline
\end{tabularx}
\caption{The parameters and results for studying capillary number region simulations.
$\delta_{\mathrm{lit}}$ is the film thickness with corresponding $Ca_{\mathrm{lit}}$ taken from
literature. $\delta_{sim}$ is the simulation film thickness with corresponding $Ca$. $U_b$ is the
center bubble velocity taken at location $x$. $Ca$ is based on the measured center bubble velocity
$U_{b}$.
\label{table:parameters:capillary:number}}
\end{table}

@@

Next, we investigated the qualitative variation of the film thickness over the bubble length.
Though there are simulations for the bubble length for the two-dimensional case, due to
the presentation of data it is hard to extract numerical values from the plots. One can see bubble lengths
variations for the two-dimensional simulations for the range of capillary numbers in Fig.
\ref{fig:sehgal:bubble:length}.
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/Bubble/bubble_sehgal.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/Bubble/bubble_length.eps}\\
\caption{The qualitative comparison for the film thickness across
the bubble length. Left (courtesy of \citet{sehgal-microchannel}),
right (present simulations). $x$ is scaled to $H_{\mathrm{eff}}$
and is taken in the flow direction.\label{fig:sehgal:bubble:length}}
\end{figure}
One can see a qualitative agreement, i.e. the thickness increases towards the front meniscus and
rapidly decreases towards the rear meniscus. This shape sometimes is referred as a "bullet" shape.

@@

\section{Conclusion}
This work presents numerical tips and a benchmark for the
Bretherton/Taylor problem using the binary liquid lattice Botlzmann method. To obtain correlations
we specifically designed the benchmark. The bubble was chosen long enough for the film thickness to
stabilize. Also, we used periodic boundary conditions for scheme robustness. Thus, the bubble
train was simulated instead of one bubble motion. To avoid the influence of other bubbles
distance between bubbles were chosen as $3$ bubble sizes. The
results show consistency with the previously published numerical results obtained
using other methods in terms of capillary number region, shape of the bubble. It comes with surprise
but with large enough viscosities ratio the results are independent on inertia. This work supports
this assumption as well. Also, we examined the influence of grid resolution on the results. We found
that if the phase interface is resolved as $50$ percent of the simulated film thickness, the results
are convergent. Though  our results are specific to the binary liquid lattice
Botlzmann method, the numerical hints and procedures can be used for any
continuous interface method.  We hope this work will prove to be valuable for
people simulating microchannel flows.
\bibliographystyle{unsrtnat}
\bibliography{paper}
